---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# RSAGA

[![Travis build status](https://travis-ci.org/r-spatial/RSAGA.svg?branch=master)](https://travis-ci.org/r-spatial/RSAGA)

Latest RSAGA version with support for SAGA GIS 2.3 LTS - 6.3.0. 

Provides access to geocomputing and terrain analysis
functions of the geographical information system (GIS) ['SAGA' (System for
Automated Geoscientific Analyses)](http://saga-gis.org/en/index.html) from within R by running the command 
line version of SAGA. This package furthermore provides several R functions
for handling ASCII grids, including a flexible framework for applying local
functions (including predict methods of fitted models) and focal functions to
multiple grids. SAGA GIS is available under GPLv2 / LGPLv2 licence from
http://sourceforge.net/projects/saga-gis/.

## Installation

You can install RSAGA 1.1.1 from CRAN with:

```{r cran-installation, eval=FALSE}
install.packages("RSAGA", dependencies = TRUE)
```

Or you can get the latest version from github with:

```{r gh-installation, eval = FALSE}
devtools::install_github("r-spatial/RSAGA")
```

Or with dependencies:

```{r gh-installation-dep, eval = FALSE}
devtools::install_github("r-spatial/RSAGA", dependencies = TRUE, force = TRUE)
```
